Legacy Data Confounds Modern Genomics Studies

### 2019-06-05 PlottingScripts/ProcessPlotData.Rmd
update

#get reverse complement of context, ref and alt
data$Rev<-ReverseComp(as.character(data$Context))
data$RevRef<-ReverseComp(as.character(data$Ref))
data$RevAlt<-ReverseComp(as.character(data$Alt))

#only get one half (to fold over)
AC<-data[which(data$Ref 
               %in% 
                 c('A','C')),]
TG<-data[which(data$Ref 
               %in% 
                 c('T','G')),]
#fold over
TG$Context <- TG$Rev
TG$Ref <- TG$RevRef
TG$Alt <- TG$RevAlt
#bind them together
data <- rbind(AC,TG)
#combine it all together to get a context
data$Mut <- paste0(data$Ref,'->', 
                substr(data$Context,1,1),
                data$Alt,
                substr(data$Context,3,3))
#get the counts of each bin
binCount <- as.data.frame(table(data$Mut))
#process for plotting
binCount$Start <- substr(binCount$Var1,4,4)
binCount$End <- substr(binCount$Var1,6,6)
binCount$Mut <- paste(substr(binCount$Var1,1,3),
                      substr(binCount$Var1,5,5))
return(binCount)
}

@@

data_fam <- fread(paste0(DataPath,
                         'Significant_Positions_allPop.fam'), 
                  col.names = c('familyID','sample',
                                'father','mother',
                                'sex','pheno')) %>%
  select(sample)

>>>>

#get reverse complement of context, ref and alt
data$Rev<-ReverseComp(as.character(data$Context))
data$RevRef<-ReverseComp(as.character(data$Ref))
data$RevAlt<-ReverseComp(as.character(data$Alt))
#only get one half (to fold over)
AC<-data[which(data$Ref 
               %in% 
                 c('A','C')),]
TG<-data[which(data$Ref 
               %in% 
                 c('T','G')),]
#fold over
TG$Context <- TG$Rev
TG$Ref <- TG$RevRef
TG$Alt <- TG$RevAlt
#bind them together
data <- rbind(AC,TG)
#combine it all together to get a context
data$Mut <- paste0(data$Ref,'->', 
                substr(data$Context,1,1),
                data$Alt,
                substr(data$Context,3,3))
#get the counts of each bin
binCount <- as.data.frame(table(data$Mut))
#process for plotting
binCount$Start <- substr(binCount$Var1,4,4)
binCount$End <- substr(binCount$Var1,6,6)
binCount$Mut <- paste(substr(binCount$Var1,1,3),
                      substr(binCount$Var1,5,5))
return(binCount)
}

@@

data_fam <- fread(paste0(DataPath,
                         'Significant_Positions_allPop.fam'), `
                  col.names = c('familyID','sample',
                                'father','mother',
                                'sex','pheno')) %>%
  select(sample)
